INTELLIGENT SYSTEMS

### 2021-04-05 paper_4.tex
finish paper4

\subsection{THE PROPOSED INTEL-TUT DATA SET}
The purpose of the dataset is to help the algorithms to determine if the color 
constancy value obtained is to be considered good or not. If an algorithm 
does not find a change in this value on the same set of images taken by the 
same camera, then this algorithm is able to have a uniform color constancy 
and consequently would produce optimal outputs.

@@

\subsubsection{Evaluation of a Direct Supervised Method}
In order to be able to calculate color constancy, and thus be able to achieve 
the camera-independence, various methods were used that included the use 
of convolutional neural networks (CNNs). In method \cite{0807099122}, the network used 
is composed of a convolutional layer with 240 filters of size 1x1, the usual 
function of ReLU, a max-Pooling of blocks of size 8x8 with stride 8. Finally 
there is a fully-connected layer with 40 layers hidden and a 3-dimensional 
output in which there is the estimated chromaticity of the lighting. In order to demonstrate the validity of the proposed dataset, the use of CNN has been adapted to the techniques described in \ref{recommend}:
\begin{enumerate}
    \item Following technique 1, various CNNs are trained to provide the least 
    possible error. The error reached by the model is less than when using 
    the Canon for training and validation. This means that the networks 
    assume the camera-independence only with the Nikon and mobile models. 
    Therefore the networks would be able to recognize new cameras. As 
    can be seen in the figure, the RAE values between the various cameras 
    are very similar (Fig. \ref{fig:CNNtec1}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper4/CNNtec1.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} with CCM on $ 1^{rst} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec1}
    \end{figure}
    \item Now a CNN is trained using technique 2. The training is carried out 
    with images acquired from both Nikon and mobile. Canon's images are 
    used for validation, while Canon's images belonging to the $ 2^{nd} $ field 
    are used for the test. Low errors are obtained with the use of a color 
    conversion matrix (CCM) \cite{0807099129} and therefore the model manages to have 
    the camera/scene-independence (Fig. \ref{fig:CNNtec2}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper4/CNNtec2.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} with CCM on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec2}
    \end{figure}
    \item According to technique 3, a CNN can be trained to reach camera independence 
    only on one camera, excluding the others. In this case, since 
    the images of the $ 2^{nd} $ field, used for both training and validation, belong 
    only to Canon, then CNN will get the camera/scene-independence 
    only on this type of camera.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper4/CNNtec3.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec2}
    \end{figure}
\end{enumerate}

@@

\subsection{CONCLUSION}

>>>>

\subsection{THE PROPOSED INTEL-TUT DATA SET}
The purpose of the dataset is to help the algorithms to determine if the color 
constancy value obtained is to be considered good or not. If an algorithm 
does not find a change in this value on the same set of images taken by the 
same camera, then this algorithm is able to have a uniform color constancy 
and consequently would produce optimal outputs. Each image in the 
dataset has undergone several changes such as: black level correction (BLC), 
color shading correction (CSC) (only for mobile camera), white balance (WB), 
color conversion from RGB sensor to sRGB (CCM) , gamma correction of 
0.45, sharpening effect correction (blur) and brightness normalization.

@@

\subsubsection{Evaluation of a Direct Supervised Method}
In order to be able to calculate color constancy, and thus be able to achieve 
the camera-independence, various methods were used that included the use 
of convolutional neural networks (CNNs). In method \cite{0807099122}, the network used 
is composed of a convolutional layer with 240 filters of size 1x1, the usual 
function of ReLU, a max-Pooling of blocks of size 8x8 with stride 8. Finally 
there is a fully-connected layer with 40 layers hidden and a 3-dimensional 
output in which there is the estimated chromaticity of the lighting. In order to demonstrate the validity of the proposed dataset, the use of CNN has been adapted to the techniques described in \ref{recommend}:
\begin{enumerate}
    \item Following technique 1, various CNNs are trained to provide the least 
    possible error. The error reached by the model is less than when using 
    the Canon for training and validation. This means that the networks 
    assume the camera-independence only with the Nikon and mobile models. 
    Therefore the networks would be able to recognize new cameras. As 
    can be seen in the figure, the RAE values between the various cameras 
    are very similar (Fig. \ref{fig:CNNtec1}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper4/CNNtec1.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} with CCM on $ 1^{rst} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec1}
    \end{figure}
    \item Now a CNN is trained using technique 2. The training is carried out 
    with images acquired from both Nikon and mobile. Canon's images are 
    used for validation, while Canon's images belonging to the $ 2^{nd} $ field 
    are used for the test. Low errors are obtained with the use of a color 
    conversion matrix (CCM) \cite{0807099129} and therefore the model manages to have 
    the camera/scene-independence (Fig. \ref{fig:CNNtec2}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper4/CNNtec2.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} with CCM on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec2}
    \end{figure}
    \item According to technique 3, a CNN can be trained to reach camera independence 
    only on one camera, excluding the others. In this case, since 
    the images of the $ 2^{nd} $ field, used for both training and validation, belong 
    only to Canon, then CNN will get the camera/scene-independence 
    only on this type of camera (Fig. \ref{fig:CNNtec3}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper4/CNNtec3.png}
        \centering
        \caption{Camera Independence of \cite{0807099122} on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
        \label{fig:CNNtec3}
    \end{figure}
\end{enumerate}

@@

\subsection{CONCLUSION}
The dataset proposed in this paper is useful for testing the behavior of an algorithm, or a model based on CNN, in the search of camera/scene-independece. If the algorithm manages to obtain this benefit, then it will be able to generalize a scene composed of several images acquired from different cameras, otherwise the results returned by this will be highly variable. Achieving this goal can also be done using a CNN if the CMM process is applied to its input set. It is necessary to specify that, in order to achieve the final result, it is essential to have the spectral sensitivities of each camera without which it would not be possible to achieve camera independence.
